---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages("formattable")

# Load in libraries
library(tidyverse)
library(ggplot2)
library(lubridate)
library(skimr)
library(psych)
library(Hmisc)
library(corrplot)
library(naniar)
library(GGally)
library(janitor)
library(formattable)

```

PRELIM CHECK - GOOGLE TRENDS DATA SETS
```{r}
# Load in data sets
global_warming <- read_csv("global_warming.csv")
global_warming %>% head()

climate_change <- read_csv("climate_change.csv")
climate_change %>% head()

buy_e_cars <- read_csv("buy_e_car.csv")
buy_e_cars %>% head()
```

PRELIM CHECK - CHARGING STATION DATA SET
```{r}
# Load in data set
charging_stations <- read_csv("charging_station.csv")
charging_stations %>% head()
```

MERGE CHARGING STATION DATA SET + GLOBAL WARMING + CLIMATE CHANGE + BUY E CAR
```{r}
# Merge charging stations with global warming
inner_join(charging_stations, global_warming, by = c("YearDate" = "Year", "MonthDate" = "Month")) -> df

# Merge new data set with climate change
inner_join(df, climate_change, by = c("YearDate" = "Year", "MonthDate" = "Month")) -> df

# Merge charging stations with buy e car
inner_join(df, buy_e_cars, by = c("YearDate" = "Year", "MonthDate" = "Month")) -> df
```

RENAME VARIABLES
```{r}
df %>%
  rename(
    "Interest_Ecar" = "Interest_GW.y",
    "Interest_GW" = "Interest_GW.x",
    "Year" = "YearDate",
    "Month" = "MonthDate"
  ) -> df

```

WRITE NEW DATA FRAME TO CSV
```{r}
write.csv(df, "/Users/angelchang/Desktop/VU/Master/P4/Modeling/Week 3/Assignment/charging_clean.csv", row.names=FALSE)
```


EDA


DESCRIPTIVES - INTENTIONS GOOGLE TRENDS
```{r}
# Interest in global warming, interest in climate change, interest in buying e-cars

df %>%
  select(Interest_GW, Interest_CC, Interest_Ecar) %>%
  summarise_all(mean) -> stats1

df %>%
  select(Interest_GW, Interest_CC, Interest_Ecar) %>%
  summarise_all(median) -> stats2

df %>%
  select(Interest_GW, Interest_CC, Interest_Ecar) %>%
  summarise_all(sd) -> stats3

df %>%
  select(Interest_GW, Interest_CC, Interest_Ecar) %>%
  summarise_all(min) -> stats4

df %>%
  select(Interest_GW, Interest_CC, Interest_Ecar) %>%
  summarise_all(max) -> stats5


# Combine all stats rows
bind_rows(stats1, stats2, stats3, stats4, stats5) -> stats_combo

colnames(stats_combo) <- c("Interest in Global Warming",
                           "Interest in Climate Change",
                           "Interest in Buying E-Cars")
```

DESCRIPTIVES - SUSTAINABILITY INTENTIONS
```{r}
# Reducing carbon intentions (from countries data set)
countries %>%
  select(yes_reduce_carbon) %>%
  summarise_all(mean) -> carbon1

countries %>%
  select(yes_reduce_carbon) %>%
  summarise_all(median) -> carbon2

countries %>%
  select(yes_reduce_carbon) %>%
  summarise_all(sd) -> carbon3

countries %>%
  select(yes_reduce_carbon) %>%
  summarise_all(min) -> carbon4

countries %>%
  select(yes_reduce_carbon) %>%
  summarise_all(max) -> carbon5


# Combine all stats rows
bind_rows(carbon1, carbon2, carbon3, carbon4, carbon5) -> carbon_combo


# Combine with other previous descriptives table
stats_combo <- cbind(carbon_combo, stats_combo)


# Reformat table
rownames(stats_combo) <- c("Mean",
                           "Median",
                           "SD",
                           "Min",
                           "Max")

stats_combo %>%
  rename(
    "Sustainable Travel Intention" = "yes_reduce_carbon"
  ) -> stats_combo

formattable(stats_combo)
  
```

DISTRIBUTIONS (BAR CHART)
```{r}
# Bar chart of number of charging station opened, grouped by year
ggplot(df, aes(x = df$Year, y = df$ChargingStations)) + geom_bar(stat = "identity", fill = "#69b3a2") +
  scale_x_continuous(breaks = df$Year) + theme_classic(base_size = 18) +
  labs(
    x = "Year",
    y = "Number of Charging Stations Opened") + coord_flip()

#df %>%
  #group_by(Year) %>%
  #summarise(nr_charging_stations = sum(ChargingStations, na.rm = T)) %>%
  #ggplot() + geom_col(aes(y = nr_charging_stations, x = Year), fill = "#69b3a2") +
  #scale_x_continuous(breaks = Year) +
  #labs(
    #x = "Year",
    #y = "Number of Charging Stations Opened") +
  #theme_classic(base_size = 12)
  # OR:
  # ggplot(aes(x = Year, y = ChargingStations)) + geom_bar(stat = "identity") + coord_flip()
```


BASIC LINE PLOT - CHARGING STATIONS & PLOTS TOTAL
```{r}
plot(df$ChargingStations, type = "o")

plot(df$PortsTotal, type = "o")

plot(df$PortsFast, type = "o")

plot(df$PortsLevel1, type = "o")

plot(df$PortsLevel2, type = "o")
```

LINE PLOTS AGAINST YEAR: CHARGING STATIONS, PORTS TOTAL, PORTS FAST
```{r}
# charging stations
ggplot(df, aes(x = df$no, y = df$ChargingStations)) +
  geom_line(color="#69b3a2", linewidth = 1, alpha = 0.9, linetype = 1) +
  theme_minimal(base_size = 16) +
  labs(
    x = "Months (March 2010 - December 2021)",
    y = "Number of Charging Stations Opened")


# ports total
ggplot(df, aes(x = df$no, y = df$PortsTotal)) +
  geom_line(color="#69b3a2", linewidth = 1, alpha = 0.9, linetype = 1) +
  theme_minimal(base_size = 16) +
  labs(
    x = "Months (March 2010 - December 2021)",
    y = "Number of Total Ports Opened")


# ports fast
ggplot(df, aes(x = df$no, y = df$PortsFast)) +
  geom_line(color="#69b3a2", linewidth = 1, alpha = 0.9, linetype = 1) +
  theme_minimal(base_size = 16) +
  labs(
    x = "Months (March 2010 - December 2021)",
    y = "Number of Fast-Charging Ports Opened")


df %>%
  filter(post_jul_18 == 1) %>%
  ggplot(aes(x = no, y = PortsFast)) +
  geom_line(color="#69b3a2", linewidth = 1, alpha = 0.9, linetype = 1) +
  theme_minimal(base_size = 16) +
  labs(
    x = "Months (July 2018 - December 2021)",
    y = "Number of Fast-Charging Ports Opened")



```

CORRELATIONS --> CHARGING STATIONS
```{r}
# Interest GW --> charging stations
## NEGATIVE
df %>%
  ggplot() + geom_point(aes(x = Interest_GW, y = ChargingStations)) +
  stat_smooth(aes(x = Interest_GW, y = ChargingStations), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Interest in Global Warming",
    y = "Number of Charging Stations Opened"
  ) + theme_classic(base_size = 15)


# Interest CC --> charging stations
## POSITIVE
df %>%
  ggplot() + geom_point(aes(x = Interest_CC, y = ChargingStations)) +
  stat_smooth(aes(x = Interest_CC, y = ChargingStations), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Interest in Climate Change",
    y = "Number of Charging Stations Opened"
  ) + theme_classic(base_size = 15)


# Interest e car --> charging stations
## POSITIVE
df %>%
  ggplot() + geom_point(aes(x = Interest_Ecar, y = ChargingStations)) +
  stat_smooth(aes(x = Interest_Ecar, y = ChargingStations), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Interest in Buying E-Cars",
    y = "Number of Charging Stations Opened"
  ) + theme_classic(base_size = 15)
```

CORRELATIONS --> PORTS FAST
```{r}
# Interest in global warming
df %>%
  ggplot() + geom_point(aes(x = Interest_GW, y = PortsTotal)) +
  stat_smooth(aes(x = Interest_GW, y = PortsTotal), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Interest in Global Warming",
    y = "Number of Total Ports Opened"
  ) + theme_minimal(base_size = 16)

# Interest in buying electric cars
df %>%
  filter(post_jul_18 == 1) %>%
  ggplot() + geom_point(aes(x = Interest_Ecar, y = PortsFast)) +
  stat_smooth(aes(x = Interest_Ecar, y = PortsFast), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Interest in Buying E-Cars After July 2018",
    y = "Number of Fast-Charging Ports Opened"
  ) + theme_minimal(base_size = 16)


```



DATA TRANSFORMATION
NEW VARIABLE CREATION



CREATE LAG VARIBLES - IV
```{r}
# Create new lag variables for interest in global warming
df %>%
  mutate(
    gw_lag_6 = lag(Interest_GW, n = 6),
    gw_lag_7 = lag(Interest_GW, n = 7),
    gw_lag_8 = lag(Interest_GW, n = 8),
    gw_lag_9 = lag(Interest_GW, n = 9),
    gw_lag_10 = lag(Interest_GW, n = 10),
    gw_lag_11 = lag(Interest_GW, n = 11),
    gw_lag_12 = lag(Interest_GW, n = 12)
  ) -> df

# Create new lag variables for interest in buying e-cars
df %>%
  mutate(
    car_lag_6 = lag(Interest_Ecar, n = 6),
    car_lag_7 = lag(Interest_Ecar, n = 7),
    car_lag_8 = lag(Interest_Ecar, n = 8),
    car_lag_9 = lag(Interest_Ecar, n = 9),
    car_lag_10 = lag(Interest_Ecar, n = 10),
    car_lag_11 = lag(Interest_Ecar, n = 11),
    car_lag_12 = lag(Interest_Ecar, n = 12)
  ) -> df

```

CREATE LAG VARIBLES - DV
```{r}
# Create lag variables for charging station DV
## By year (12 months), by monthly (1 month)
df %>%
  mutate(
    stations_lag_12 = lag(ChargingStations, n = 12),
    stations_lag_1 = lag(ChargingStations, n = 1)
    ) -> df

# Create lag variables for ports total DV
df %>%
  mutate(
    ports_lag_2 = lag(PortsTotal, n = 2),
    ports_lag_3 = lag(PortsTotal, n = 3),
    ports_lag_4 = lag(PortsTotal, n = 4),
    ports_lag_5 = lag(PortsTotal, n = 5)
    ) -> df

# Create lag variables for ports fast DV
df %>%
  mutate(
    ports_fast_lag_2 = lag(PortsFast, n = 2),
    ports_fast_lag_3 = lag(PortsFast, n = 3)) -> df

```

CREATE OTHER NEW VARIABLES
```{r}
# Dummy variables for structural breaks
## September 2017
df %>%
  mutate(
    post_sep_17 = ifelse(Year >= 2018, 1, 0) # Separate values from 2018 onwards first
  ) -> df

# Change dummy values to 1 for Sep, Oct, Nov, Dec 2017
df$post_sep_17[df$Year == 2017 & df$Month == 9] <- 1
df$post_sep_17[df$Year == 2017 & df$Month == 10] <- 1
df$post_sep_17[df$Year == 2017 & df$Month == 11] <- 1
df$post_sep_17[df$Year == 2017 & df$Month == 12] <- 1


## July 2018
df %>%
  mutate(
    post_jul_18 = ifelse(Year >= 2019, 1, 0) # Separate values from 2019 onwards first
  ) -> df

# Change dummy values to 1 for Jul, Aug, Sep, Oct, Nov, Dec 2018
df$post_jul_18[df$Year == 2018 & df$Month == 7] <- 1
df$post_jul_18[df$Year == 2018 & df$Month == 8] <- 1
df$post_jul_18[df$Year == 2018 & df$Month == 9] <- 1
df$post_jul_18[df$Year == 2018 & df$Month == 10] <- 1
df$post_jul_18[df$Year == 2018 & df$Month == 11] <- 1
df$post_jul_18[df$Year == 2018 & df$Month == 12] <- 1
```

REFORMAT DATA FRAME
```{r}
# Move column positions
df %>% relocate(post_sep_17, post_jul_18, .after = PortsTotal) -> df

# Remove ports levels 1 and 2
df %>% select(-PortsLevel1, -PortsLevel2) -> df

# Remove interest in climate change
df %>% select(-Interest_CC) -> df

```

WRITE NEW DATA FRAME (WITH NEW VARIABLES) TO CSV
```{r}
write.csv(df, "/Users/angelchang/Desktop/VU/Master/P4/Modeling/Week 3/Assignment/charging_final.csv", row.names=FALSE)
```

