---
title: "R Notebook"
output: html_notebook
---

LOAD IN LIBRARIES & DATA SET
```{r}

install.packages("car")

# Load in libraries
library(tidyverse)
library(ggplot2)
library(lubridate)
library(Hmisc)
library(naniar)
library(GGally)
library(janitor)
library(formattable)
library(jtools) # Summarizing regression output, effect_plot
library(broom) # Tidying and augmenting model output
library(margins) # Marginal effects
library(ggfortify)
library(stargazer)
library(modelsummary)
library(car)

# Load in data
data <- read_csv("charging_final.csv")
```

CHARGING STATIONS AS DV
```{r}
# IVs - interest in global warming, interest in e-cars
data %>%
  lm(ChargingStations ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags)
data %>%
  lm(ChargingStations ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12,
     data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags), sep 2017 break
data %>%
  lm(ChargingStations ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12 +
       post_sep_17,
     data = .) %>%
  summ(digits = 3)
```

CHARGING STATIONS AS DV - MOST SIGNIFICANT LAGS
```{r}
# gw_lag_6, car_lag_6, car_lag_10, car_lag_11
data %>%
  lm(ChargingStations ~ gw_lag_6 + car_lag_6 + car_lag_10 + car_lag_11, data = .) %>%
  summ(digits = 3)

```

CHARGING STATIONS AS DV (LAGGED)
```{r}
# IVs - interest in global warming, interest in e-cars
data %>%
  lm(stations_lag_12 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)

data %>%
  lm(stations_lag_1 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags)
data %>%
  lm(stations_lag_12 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags), sep 2017 break
data %>%
  lm(stations_lag_1 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12 +
       post_sep_17,
     data = .) %>%
  summ(digits = 3)
```

CHARGING STATIONS AS DV (LAGGED) - MOST SIGNIFICANT
```{r}
# car_lag_7, car_lag_12
data %>%
  lm(stations_lag_12 ~ car_lag_7 + car_lag_12, data = .) %>%
  summ(digits = 3)

data %>%
  lm(stations_lag_1 ~ Interest_GW + Interest_Ecar + post_sep_17, data = .) %>%
  summ(digits = 3)

```

PORTS TOTAL AS DV
```{r}
# IVs - interest in global warming, interest in e-cars
data %>%
  lm(PortsTotal ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags)
data %>%
  lm(PortsTotal ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12,
     data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags), sep 2017 break
data %>%
  lm(PortsTotal ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12 +
       post_sep_17,
     data = .) %>%
  summ(digits = 3)
```

PORTS TOTAL AS DV - MOST SIGNIFICANT LAGS
```{r}
# gw_lag_6, car_lag_10, car_lag_11, car_lag_12
data %>%
  lm(PortsTotal ~ gw_lag_6 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)


```

PORTS TOTAL AS DV (LAGGED)
```{r}
# IVs - interest in global warming, interest in e-cars
data %>%
  lm(ports_lag_2 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)

data %>%
  lm(ports_lag_3 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)

data %>%
  lm(ports_lag_4 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)

data %>% # BEST
  lm(ports_lag_5 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)



# IVs - interest in global warming (lags), interest in e-cars (lags)
data %>%
  lm(ports_lag_2 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)

data %>%
  lm(ports_lag_3 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)

data %>%
  lm(ports_lag_4 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)

data %>% # BEST
  lm(ports_lag_5 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)



# IVs - interest in global warming (lags), interest in e-cars (lags), sep 2017 break
data %>%
  lm(ports_lag_5 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12 +
       post_sep_17,
     data = .) %>%
  summ(digits = 3)
```

PORTS TOTAL AS DV (LAGGED) - MOST SIGNIFICANT
```{r}
# gw_lag_10, car_lag_7, car_lag_10, car_lag_11
data %>% # BEST
  lm(ports_lag_5 ~ gw_lag_10 + car_lag_7 + car_lag_10 + car_lag_11, data = .) %>%
  summ(digits = 3)


data %>%
  lm(ports_lag_5 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)

```

PORTS FAST AS DV
```{r}
# IVs - interest in global warming, interest in e-cars
data %>%
  lm(PortsFast ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags)
data %>%
  lm(PortsFast ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12,
     data = .) %>%
  summ(digits = 3)


# IVs - interest in global warming (lags), interest in e-cars (lags), sep 2017 break
data %>%
  lm(PortsFast ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12 +
       post_jul_18,
     data = .) %>%
  summ(digits = 3)
```

FINAL MODEL CHOSEN FOR REPORT
```{r}
data %>%
  lm(PortsFast ~ car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 +
       gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 +
       post_jul_18,
     data = .) -> model
  # summ(digits = 3)


stargazer(model, type = "html", out = "cars.html")


# assumption mean error check
residuals1 <- resid(model)
summary(residuals1)


# homoskedasticity - variance of residuals is not hetero
plot(residuals1)
ncvTest(model)


# multicollinear
vif(model)


# autocorrelation
acf(residuals1)
durbinWatsonTest(model)


# check for error distribution - normal?
hist(df$PortsFast)
qqnorm(resid(model))


# robustness check - alternative model
data %>%
  lm(PortsFast ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 + car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 +car_lag_11 +car_lag_12,
     data = .) %>% summ(digits = 3)
## adding lag 6, 7, 12 were not significant, and did not make lags 8, 9, 10 less significant, so model is robust



```

***PORTS FAST AS DV - MOST SIGNIFICANT LAGS***
```{r}
# gw_lag_9, gw_lag_10, car_lag_7, car_lag_8, car_lag_9, car_lag_10, post_jul_18
data %>%
  lm(PortsFast ~ gw_lag_9 + gw_lag_10 + car_lag_7 + car_lag_8 + car_lag_9 +
       car_lag_10 + post_jul_18, data = .) %>%
  summ(digits = 3)


```

PORTS FAST AS DV (LAGGED)
```{r}
# IVs - interest in global warming, interest in e-cars
data %>%
  lm(ports_fast_lag_2 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)

data %>% # BEST
  lm(ports_fast_lag_3 ~ Interest_GW + Interest_Ecar, data = .) %>%
  summ(digits = 3)



# IVs - interest in global warming (lags), interest in e-cars (lags)
data %>%
  lm(ports_fast_lag_2 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)

data %>%
  lm(ports_fast_lag_3 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12, data = .) %>%
  summ(digits = 3)



# IVs - interest in global warming (lags), interest in e-cars (lags), jul 2018 break
data %>%
  lm(ports_fast_lag_2 ~ gw_lag_6 + gw_lag_7 + gw_lag_8 + gw_lag_9 + gw_lag_10 + gw_lag_11 + gw_lag_12 +
       car_lag_6 + car_lag_7 + car_lag_8 + car_lag_9 + car_lag_10 + car_lag_11 + car_lag_12 +
       post_jul_18,
     data = .) %>%
  summ(digits = 3)
```

PORTS FAST AS DV (LAGGED) - MOST SIGNIFICANT
```{r}
# gw_lag_11, gw_lag_12, car_lag_6, car_lag_9, car_lag_10, car_lag_11, post_jul_18
data %>%
  lm(ports_fast_lag_2 ~ gw_lag_11 + gw_lag_12 + car_lag_6 + car_lag_9 + car_lag_10 + car_lag_11 + post_jul_18,
     data = .) %>%
  summ(digits = 3)

```

